---
title: "ÖFG Auswertung"
author: "Lena"
date: "2026-08-12"
output:
  pdf_document: 
    latex_engine: xelatex

---

# 1 - Load packages
```{r packages}
library(dplyr)
library(tidyr)
library(lubridate)
library(writexl) # noch nicht benutzt
library(readxl) 
library(ggplot2)
library(ggrepel) # annotations in plot
library(patchwork) 
#library(broom) # noch nicht benutzt
#library(leaflet) # for interactive map
#library(leaflet.providers) # satellite as background for interactive map
#library(sf) # convert lat/lon to geodata
#library(maptiles) # for open street map
#library(tidyterra) # for basemap plot
#library(cowplot) # for small map inlay
#library(rnaturalearth) # for overview map
#library(rnaturalearthdata) # for overview map
#library(forcats)
library(purrr)
```


# 2 - Data import

```{r}

##Paste the location of your import file, name of sheet should be DATA

excel_path <- "~/Seafile/ÖFG 150/2 Daten/Rohdaten Gesamt/2000_Alle Daten.xlsx"

sheet_name <- "DATA"

##Excel is loaded into R and cleaned

raw_excel <- read_excel(excel_path, sheet = sheet_name, col_types = "text")

data <- raw_excel %>% 
  janitor::clean_names()

rm(raw_excel)
  

# Numeric robust aus Text (Komma/Punkt etc.)
to_num <- function(x) {
  x_chr <- as.character(x)
  x_chr <- gsub(",", ".", x_chr)
  x_chr <- gsub("[^0-9\\+\\-\\.eE]", "", x_chr)
  suppressWarnings(as.numeric(x_chr))
}


## load data in the correct format

data <- data %>%
  mutate(
    # --- Date ---
    date = as.Date(as.numeric(date), origin ="1899-12-30"),

    # --- Character ---
    data_provider      = as.character(data_provider),
    remark_raw_data           = as.character(remark_raw_data),
    remark_import             = as.character(remark_import),
    pit_dec                   = as.character(pit_dec),
    pit_hex                   = as.character(pit_hex),
    
    #Faktor
    country            = as.factor(country),
    river_name         = as.factor(river_name),
    source             = as.character(source),
    project            = as.factor(project),
    site_name          = as.factor(site_name),
    method             = as.factor(method),
    sampling_time      = as.factor(sampling_time),
    assessment         = as.factor(assessment),
    sample_id          = as.factor(sample_id),
    species            = as.factor(species),
    habitat            = as.factor(habitat),
    fishing_district    = as.factor(fishing_district),
    preclassification_stressor =  as.factor(preclassification_stressor),
    type_of_strip             = as.factor(type_of_strip),
    reader_id                 = as.factor(reader_id),

    # --- Numeric ---
    year               = to_num(year),
    landmark_up        = to_num(landmark_up),
    lat_up             = to_num(lat_up),
    long_up            = to_num(long_up),
    landmark_down      = to_num(landmark_down),
    lat_down           = to_num(lat_down),
    long_down          = to_num(long_down),
    temp               = to_num(temp),
    anodes             = to_num(anodes),
    fished_length      = to_num(fished_length),
    fished_width       = to_num(fished_width),
    fish_id            = to_num(fish_id),
    total_length       = to_num(total_length),
    weight             = to_num(weight),
    length_site         = to_num(length_site),
    width_site          = to_num(width_site),
    conductivity        = to_num(conductivity),
    p_h_value             = to_num(p_h_value),
    ox_cont             = to_num(ox_cont),
    ox_sat              = to_num(ox_sat),
    mean_water_depth    = to_num(mean_water_depth),
    discharge           = to_num(discharge),
    catch_efficiency    = to_num(catch_efficiency),
    memory_id           = to_num(memory_id),

    # --- Logical (TRUE/FALSE) ---

    recapture                 = as.logical(recapture),
    approval_required  = as.logical(approval_required)
    

  )



str(data)


#output for data


#output directory for plots

dir.create("plots", showWarnings = FALSE)




```

# 3 - Load Functions

```{r}

#Seber-LeCren 

## working

seber_le_cren_est <- function(C1, C2) {
  
  C1 <- as.numeric(C1)[1]
  C2 <- as.numeric(C2)[1]
  
  if (!is.finite(C1) || !is.finite(C2)) {
    return(tibble(
      N = NA_real_,
      Var_N = NA_real_,
      sd_N = NA_real_,
      CI_95 = NA_real_,
      N_min = NA_real_,
      N_max = NA_real_,
      ok = FALSE,
      msg = "Missing or non-numeric C1/C2"
    ))
  }
  
  if (C1 <= 0) {
    return(tibble(
      N = NA_real_,
      Var_N = NA_real_,
      sd_N = NA_real_,
      CI_95 = NA_real_,
      N_min = NA_real_,
      N_max = NA_real_,
      ok = FALSE,
      msg = "C1 must be > 0"
    ))
  }
  
  if (C2 >= C1) {
    return(tibble(
      N = NA_real_,
      Var_N = NA_real_,
      sd_N = NA_real_,
      CI_95 = NA_real_,
      N_min = NA_real_,
      N_max = NA_real_,
      ok = FALSE,
      msg = "C2 must be smaller than C1"
    ))
  }
  
  N <- C1^2 / (C1 - C2)
  Var_N <- (C1^2 * C2^2 * (C1 + C2)) / (C1 - C2)^4
  sd_N <- sqrt(Var_N)
  CI_95 <- 2 * sd_N
  
  tibble(
    N = round(N, 0),
    Var_N = round(Var_N, 2),
    sd_N = round(sd_N, 1),
    CI_95 = round(CI_95, 0),
    N_min = round(N - CI_95, 0),
    N_max = round(N + CI_95, 0),
    ok = TRUE,
    msg = NA_character_
  )
}

#DeLury 
delury_est <- function(counts) {
  
  counts <- as.numeric(counts)

  out_na <- function(msg, N = NA_real_) {
    tibble(
      N     = N,
      Var_N = NA_real_,
      sd_N  = NA_real_,
      CI_95 = NA_real_,
      N_min = NA_real_,
      N_max = NA_real_,
      ok    = FALSE,
      msg   = msg
    )
  }
  #checks for missing or non numeric values
  if (any(!is.finite(counts))) {
    return(out_na("Missing or non-numeric counts"))
  }
  
  #checks number of runs
  if (length(counts) < 3) {
    return(out_na("DeLury needs >= 3 passes"))
  }
  
  #checks if catches are positive
  if (any(counts < 0)) {
    return(out_na("Counts must be >= 0"))
  }
  
  #checks if catches are zero
  if (sum(counts) == 0) {
    return(out_na("No fish caught"))
  }
  
  #checks varation in runs - catches must be different for each run
  if (length(unique(counts)) < 2) {
    return(out_na("No depletion (all counts equal)"))
  }
  
  # y = catches in run, x = cumulative catch before run
  df <- tibble(
    catch        = counts,
    CumCatchPrev = c(0, cumsum(counts)[-length(counts)])
  )
  
  #checks if linear model can be fitted
  fit <- try(lm(catch ~ CumCatchPrev, data = df), silent = TRUE)
  
  if (inherits(fit, "try-error")) {
    return(out_na("LM failed"))
  }
  
  a <- unname(coef(fit)["(Intercept)"])
  b <- unname(coef(fit)["CumCatchPrev"])
  
  #checks if coefficients are valid
  if (!is.finite(a) || !is.finite(b)) {
    return(out_na("Coefficients could not be estimated"))
  }
  
  #checks if slope is negative
  if (b >= 0) {
    return(out_na("Slope must be negative (no depletion)"))
  }
  
  #checks if intercept is positive
  if (a <= 0) {
    return(out_na("Intercept must be > 0"))
  }
  
  #Estimate of population
  N <- a / (-b)
  
  #checks if estimated N is bigger than real catch
  if (N < sum(counts)) {
    return(out_na("N smaller than total catch", N = round(N, 0)))
  }
  
  # Calculate variance Delta Method - kann man das so machen?
  vc    <- vcov(fit)
  dN_da <- -1 / b
  dN_db <-  a / b^2
  
  Var_N <- dN_da^2 * vc[1, 1] +
           dN_db^2 * vc[2, 2] +
           2 * dN_da * dN_db * vc[1, 2]
  
  #checks if variance can be calculated 
  if (!is.finite(Var_N) || Var_N < 0) {
    return(out_na("Variance could not be estimated", N = round(N, 0)))
  }
  
  sd_N  <- sqrt(Var_N)
  CI_95 <- 2 * sd_N
  
#return of results 
  tibble(
    N     = round(N, 0),
    Var_N = round(Var_N, 2),
    sd_N  = round(sd_N, 1),
    CI_95 = round(CI_95, 0),
    N_min = round(N - CI_95, 0),
    N_max = round(N + CI_95, 0),
    ok    = TRUE,
    msg   = NA_character_
  )
}



```

#/
#4 - Overview over sites fished -(number of species, individuals of species, totals)


```{r}

#add row for each species and number of species for each site

overview_data <- data %>% 
  filter(!is.na(site_name), !is.na(species)) %>% 
  group_by(river_name, site_name, species) %>% 
  summarise(
    Stelle = first(site_name), 
    `Befischte_Länge(m)` = first(fished_length),
    n_individuals = n(),
    .groups = "drop"
  ) %>% 
  pivot_wider(
    names_from = species, 
    values_from = n_individuals, 
    values_fill = 0
  )

#extract species names 
species_cols <- setdiff(
  names(overview_data), 
  c("site_name", "river_name", "Stelle", "Befischte_Länge(m)")
)

#Summarize number of total individuals per site and number of different species 
overview_data <- overview_data %>% 
  mutate(
    Anzahl_Arten = rowSums(across(all_of(species_cols)) > 0, na.rm = TRUE), 
    Gesamtfangzahl = rowSums(across(all_of(species_cols)), na.rm = TRUE)
  ) %>% 
    select(-site_name) %>% 
    relocate(Anzahl_Arten, Gesamtfangzahl, .after = Stelle)

#Summarize total number of fish of each species, total number of different species in sampling campain, total length fished, total number of fish caught

total_row_species_data <- overview_data %>% 
  summarise(
    Fluss = "Total",
    `Befischte_Länge(m)` = sum(`Befischte_Länge(m)`, na.rm = TRUE), 
    Anzahl_Arten = sum(colSums(across(all_of(species_cols)), na.rm = TRUE) > 0),
    Gesamtfangzahl = sum(Gesamtfangzahl, na.rm = TRUE), 
    across(all_of(species_cols), ~ sum(.x, na.rm = TRUE))
  )
  
# bind rows 
overview_data <- bind_rows(overview_data, total_row_species_data)

# remove total row

rm(total_row_species_data)

# show table

overview_data






```
## 4.1. Export to xlsx.

```{r}
# Write outputs ----> add your output path and desired name of excel document

#out_path <- "C:/Users/lenagraf/Documents/Seafile/ÖFG 150/4 Auswertungen/Overview_species_list_V2.xlsx"

#writexl::write_xlsx(
 # list(
  #  overview = overview_data
  #),
  #path = out_path
#)

#Done


```


#/
# 5 - Seber-LeCren

## 5.1. Prepare Data for Seber-LeCren or DeLury

```{r}

#Summarize Data to get number of species per Site and number of species per Run in seperate columns

##Extract Number of Individuals per Species per run and site and total weight

dat_summary <- data %>%
  count(site_name, species, sample_id) %>% 
  pivot_wider(
    names_from = sample_id, 
    values_from = n, 
    names_glue = "Run_{sample_id}", 
    values_fill = 0
  ) %>%
  mutate(
    species_total = rowSums(across(any_of(c("Run_1", "Run_2", "Run_3"))), na.rm = TRUE)
  ) 

## Calculate weight per species per site 


dat_weight_species_sites <- data %>% 
  group_by(site_name, species) %>% 
  summarise(
    weight_g = round(sum(weight, na.rm = TRUE), 1),
    weight_kg = round(weight_g / 1000, 2),
    median_species_weight_g = round(median(weight, na.rm = TRUE),3),
    .groups = "drop"
  )


#add median weight of all species per site 

dat_weight_site <- data %>% 
  group_by(site_name) %>% 
  summarise(
    median_weight_g_site = round(median(weight), 3), 
    .groups = "drop"
  )
  

## Add all other data 

dat_metadata <- data %>% 
  group_by(site_name, species) %>% 
  summarise(
    across(
      -c(sample_id, fish_id, total_length, weight, reader_id, pit_dec, pit_hex, remark_raw_data, remark_import), 
      first
    ),
      .groups = "drop"
  ) %>% 
  mutate(
    fished_area = fished_length * fished_width,
    area_ha = fished_area / 10000
  )

##Put metadata back to dat

dat <- dat_metadata %>% 
  left_join(dat_summary, by = c("site_name", "species")) %>% 
  left_join(dat_weight_species_sites, by = c("site_name", "species")) %>% 
  left_join(dat_weight_site, by = "site_name")

## Remove unneeded dfs 

rm(dat_summary, dat_weight_species_sites, dat_weight_site, dat_metadata)

# Working fields
run_cols <- grep("^Run_", names(dat), value = TRUE)


```

## 5.1.2. Filter Data.

```{r}

#Summarize Data to get number of species per Site and number of species per Run in seperate columns


## if needed - filter data

data_filtered <- data %>% 
    filter(!as.character(species) %in% c("Cottus gobio", "Phoxinus phoxinus", "Gobio gobio", "Barbatula barbatula", "Alburnoides bipunctatus")) %>% 
  filter(total_length > 75)  

##Extract Number of Individuals per Species per run and site and total weight


dat_summary_75 <- data_filtered %>%
  count(site_name, species, sample_id) %>% 
  pivot_wider(
    names_from = sample_id, 
    values_from = n, 
    names_glue = "Run_{sample_id}", 
    values_fill = 0
  ) %>%
  mutate(
    species_total = rowSums(across(any_of(c("Run_1", "Run_2", "Run_3"))), na.rm = TRUE)
  ) 

## Calculate weight per species per site 


dat_weight_species_sites_75 <- data_filtered %>% 
  group_by(site_name, species) %>% 
  summarise(
    weight_g = round(sum(weight, na.rm = TRUE), 1),
    weight_kg = round(weight_g / 1000, 2),
    median_species_weight_g = round(median(weight, na.rm = TRUE),3),
    .groups = "drop"
  )


## Add all other data 

dat_metadata <- data_filtered %>% 
  group_by(site_name, species) %>% 
  summarise(
    across(
      -c(sample_id, fish_id, total_length, weight, reader_id, pit_dec, pit_hex, remark_raw_data, remark_import), 
      first
    ),
      .groups = "drop"
  ) %>% 
  mutate(
    fished_area = fished_length * fished_width,
    area_ha = fished_area / 10000
  )

##Put metadata back to dat

dat_75 <- dat_metadata %>% 
  left_join(dat_summary_75, by = c("site_name", "species")) %>% 
  left_join(dat_weight_species_sites_75, by = c("site_name", "species"))
## Remove unneeded dfs 

rm(dat_summary_75, dat_weight_species_sites_75, dat_metadata)

# Working fields
run_cols <- grep("^Run_", names(dat_75), value = TRUE)


```


#/
##5.2. - Abundance per Species

```{r}


#Calculate estimated abundance, sd, CI, Var_N and N_min, N_max
## all lengths


slc_species <- dat_75 %>%
  filter(assessment == "Seber-LeCren") %>% 
  mutate(
    C1 = as.numeric(Run_1),
    C2 = as.numeric(Run_2),
    est = map2(C1, C2, seber_le_cren_est)
  ) %>%
  unnest(est)



## Calculate estimates of abundance on species and site level per area and length



slc_species <- slc_species %>% 
  mutate(
    #total number of individuals per site and species
    N_real = C1 + C2, 
    #number of estimated individuals per site and species
    N_estimate = ifelse(ok, pmax(N-N_real, 0), NA_real_), 
    #weight of estimated (extra) fish 
    weight_calc_kg = N_estimate * median_species_weight_g / 1000, 
    #total biomass per site and species 
    biomass_total_kg = weight_kg + weight_calc_kg,
    #N per ha 
    N_per_ha = ifelse(ok & area_ha > 0, N / area_ha, NA_real_), 
    #N per 100 meter
    N_per_100m = ifelse(ok & fished_length > 0, N / fished_length * 100, NA_real_), 
    # Biomass per ha (kg)
    biomass_kg_ha = ifelse(ok & area_ha > 0, biomass_total_kg / area_ha, NA_real_), 
    #Biomass per 100 m (kg)
    biomass_per_100m_kg = ifelse(ok & fished_length > 0, biomass_total_kg / fished_length * 100, NA_real_)
  )


slc_species

```

####5.2.1. Reorganize for output

```{r}
#round values 

slc_species_output <- slc_species %>%
  mutate(
    N = round(N, 0),
    N_min = round(N_min, 0),
    N_max = round(N_max, 0),
    Var_N = round(Var_N, 2),
    sd_N = round(sd_N, 1),
    CI_95 = round(CI_95, 0),

    N_per_ha = round(N_per_ha, 0),
    N_per_100m = round(N_per_100m, 0),

    weight_kg = round(weight_kg, 3),
    weight_calc_kg = round(weight_calc_kg, 3),
    biomass_total_kg = round(biomass_total_kg, 3),
    biomass_kg_ha = round(biomass_kg_ha, 2),
    biomass_per_100m_kg = round(biomass_per_100m_kg, 2)
  )

```



### 5.2.2. Site Level: Abundance and Biomass


```{r}

# Estimates for all species for each site. Estimates calculated by Seber LeCren
# For biomass sum of weight of calculated N per species is used. 
### for Ögf only bigger than 75cm - check!  

slc_site <- slc_species %>% 
  filter(assessment == "Seber-LeCren") %>% 
  group_by(river_name, site_name) %>% 
  summarise(
    C1_site = sum(C1, na.rm = TRUE), 
    C2_site = sum(C2, na.rm = TRUE), 
    fished_length = first(fished_length), 
    fished_width = first(fished_width), 
    fished_area = first(fished_area), 
    area_ha = first(area_ha), 
    n_species = n_distinct(species), 
    weight_real_kg = sum(weight_kg, na.rm = TRUE), 
    biomass_species_sum_kg = sum(biomass_total_kg, na.rm = TRUE), 
    species_total = first(species_total),
    .groups = "drop"
  ) %>% 
  mutate(
    est = map2(C1_site, C2_site, seber_le_cren_est)
  ) %>% 
  unnest(est) %>% 
  mutate(
    #Abundance estimates per ha, 100 meter 
    N_site = N,
    N_per_ha = ifelse(area_ha >0, N_site / area_ha, NA_real_), 
    N_per_100m = ifelse(fished_length > 0, N_site / fished_length * 100, NA_real_), 
    #Biomass estimates per ha, 100 meter
    biomass_kg_ha = ifelse(area_ha > 0, biomass_species_sum_kg / area_ha, NA_real_), 
    biomass_per_100m_kg = ifelse(fished_length > 0, biomass_species_sum_kg / fished_length * 100, NA_real_)
  )

#Show Output

slc_site

```





#### 5.2.3.Reorganize for output 

```{r}

#round

slc_site_output <- slc_site %>%
  mutate(
    N_site = round(N_site, 0),
    N_min = round(N_min, 0),
    N_max = round(N_max, 0),

    N_per_ha = round(N_per_ha, 0),
    N_per_100m = round(N_per_100m, 0),
    
    weight_real_kg = round(weight_real_kg, 3),
    biomass_species_sum_kg = round(biomass_species_sum_kg, 3),
    biomass_kg_ha = round(biomass_kg_ha, 2),
    biomass_per_100m_kg = round(biomass_per_100m_kg, 2)
  )





```

### 5.2.4 Export output of stock calculation to excel
```{r}


# Write outputs ----> add your output path and desired name of excel document

out_path <- "C:/Users/lenagraf/Documents/Seafile/ÖFG 150/4 Auswertungen/Stock_Calculations_all.xlsx"

writexl::write_xlsx(
  list(
    per_species = slc_species_output,
    per_site    = slc_site_output
  ),
  path = out_path
)

#Done

```



### 5.2.5 Mean Abundance and Biomass on river level

##### 5.2.5.1.Mean Abundance and Biomass for each river

```{r}

#Calculate mean abundance and biomass for each river - each site per river represented in equal proportions 

mean_river_est_site <- slc_site %>% 
  group_by(river_name) %>% 
  summarise(
    N_sites = n(), 
    N_per_ha_mean = mean(N_per_ha, na.rm = TRUE), 
    sd_N_per_ha = sd(N_per_ha, na.rm = TRUE), 
    N_per_100m_mean = mean(N_per_100m,na.rm = TRUE),
    sd_N_per_100m = sd(N_per_100m, na.rm = TRUE), 
    biomass_kg_ha_mean = mean(biomass_kg_ha, na.rm = TRUE), 
    sd_biomass_kg_ha = sd(biomass_kg_ha, na.rm = TRUE), 
    biomass_per_100m_kg_mean = mean(biomass_per_100m_kg, na.rm = TRUE),
    sd_biomass_per_100m_kg = sd(biomass_per_100m_kg, na.rm = TRUE),
    .groups = "drop"
  )

#Show output


mean_river_est_site




```





###5.2.6. Mean Abundance and Biomass for each river per species

```{r}


#Calculate mean abudance and biomass for each river for each species each site per river represented in equal proportions 
##take into account all sites, sites with 0 individuals of a species will be calculated into the mean, would be nice, not working right now. 

slc_species_site <- slc_species %>%
  filter(ok) %>%
  group_by(river_name, site_name, species) %>%
  summarise(
    N = first(N),
    N_per_ha = first(N_per_ha),
    N_per_100m = first(N_per_100m),
    biomass_kg_ha = first(biomass_kg_ha),
    biomass_per_100m_kg = first(biomass_per_100m_kg),
    .groups = "drop"
  )

species_all_sites <- slc_species_site %>%
  group_by(river_name) %>%
  complete(
    site_name,
    species,
    fill = list(
      N = 0,
      N_per_ha = 0,
      N_per_100m = 0,
      biomass_kg_ha = 0,
      biomass_per_100m_kg = 0
    )
  ) %>%
  ungroup()



mean_river_est_species <- slc_species %>% 
  group_by(river_name, species) %>% 
  summarise(
    n_sites = n_distinct(site_name),
    species_totals_mean = round(mean(species_total, na.rm = TRUE), 0), 
    N_per_ha_mean = mean(N_per_ha, na.rm = TRUE), 
    sd_N_per_ha = sd(N_per_ha, na.rm = TRUE), 
    N_per_100m_mean = mean(N_per_100m,na.rm = TRUE),
    sd_N_per_100m = sd(N_per_100m, na.rm = TRUE), 
    biomass_kg_ha_mean = mean(biomass_kg_ha, na.rm = TRUE), 
    sd_biomass_kg_ha = sd(biomass_kg_ha, na.rm = TRUE), 
    biomass_per_100m_kg_mean = mean(biomass_per_100m_kg, na.rm = TRUE),
    sd_biomass_per_100m_kg = sd(biomass_per_100m_kg, na.rm = TRUE),
    .groups = "drop"
  )

#Show table 
mean_river_est_species




```

##### 5.2.6.1. Round and save as .xlsx 

```{r}

##round output for river and all species means 

mean_river_est_site_output <- mean_river_est_site %>% 
  mutate(
    N_per_ha_mean = round(N_per_ha_mean, 0), 
    sd_N_per_ha = round(sd_N_per_ha, 0), 
    N_per_100m_mean = round(N_per_100m_mean,0),
    sd_N_per_100m = round(sd_N_per_100m, 0), 
    biomass_kg_ha_mean = round(biomass_kg_ha_mean, 2), 
    sd_biomass_kg_ha = round(sd_biomass_kg_ha, 2), 
    biomass_per_100m_kg_mean = round(biomass_per_100m_kg_mean, 2),
    sd_biomass_per_100m_kg = round(sd_biomass_per_100m_kg, 2),
  )



mean_river_est_species_output <- mean_river_est_species %>% 
  mutate(
    N_per_ha_mean = round(N_per_ha_mean, 0), 
    sd_N_per_ha = round(sd_N_per_ha, 0), 
    N_per_100m_mean = round(N_per_100m_mean,0),
    sd_N_per_100m = round(sd_N_per_100m, 0), 
    biomass_kg_ha_mean = round(biomass_kg_ha_mean, 2), 
    sd_biomass_kg_ha = round(sd_biomass_kg_ha, 2), 
    biomass_per_100m_kg_mean = round(biomass_per_100m_kg_mean, 2),
    sd_biomass_per_100m_kg = round(sd_biomass_per_100m_kg, 2),
  )

# Write outputs ----> add your output path and desired name of excel document

#out_path <- "C:/Users/lenagraf/Documents/Seafile/ÖFG 150/4 Auswertungen/mean_stock_per_river.xlsx"

#writexl::write_xlsx(
 # list(
  #  mean_species = mean_river_est_species_output,
   # mean_site    = mean_river_est_site_output
 # ),
#  path = out_path
#)

mean_river_est_site_output

mean_river_est_species_output

```



###5.6.5.Bar Charts for specific species

####5.6.5.1. Bachforelle

```{r}
#Bachforelle 

river_order <- sort(unique(mean_river_est_species_output$river_name))


# - Total Individuals per ha

bar_N_ha_bf <-  ggplot(mean_river_est_species_output %>% 
                         filter(species == "Salmo trutta"),
                       aes(x = river_name, y = N_per_ha_mean)) + 
  geom_col(fill = "grey") + 
  geom_errorbar(
    aes(
      ymin = N_per_ha_mean - sd_N_per_ha, 
      ymax = N_per_ha_mean + sd_N_per_ha
    ), 
    width = 0.2
  ) + 
  scale_x_discrete(limits = river_order) +
  labs(
    x = NULL,
    y = "[Individuen/ha]", 
    title = "Individuendichte der Bachforelle pro Hektar"
  ) +
  theme_bw() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

  
  # - Total Individuals per 100 m 
bar_N__100_bf <- ggplot(mean_river_est_species_output %>% 
                          filter(species == "Salmo trutta"),
                        aes(x = river_name, y = N_per_100m_mean)) + 
  geom_col(fill = "grey") + 
  geom_errorbar(
    aes(
      ymin = N_per_100m_mean - sd_N_per_100m, 
      ymax = N_per_100m_mean + sd_N_per_100m
    ), 
    width = 0.2
  ) + 
  scale_x_discrete(limits = river_order) +
  labs(
    x= NULL, 
    y = "[Individuen/100m]", 
    title = "Individuendichte der Bachforelle pro 100 m"
  ) +
  theme_bw() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )



  # - Total Biomass ka / ha

bar_bio_ha_bf <- ggplot(mean_river_est_species_output %>% 
                          filter(species == "Salmo trutta"),
                        aes(x = river_name, y = biomass_kg_ha_mean)) + 
  geom_col(fill = "grey") + 
  geom_errorbar(
    aes(
      ymin = pmax(biomass_kg_ha_mean - sd_biomass_kg_ha, 0), 
      ymax = biomass_kg_ha_mean + sd_biomass_kg_ha
    ), 
    width = 0.2
  ) + 
  scale_x_discrete(limits = river_order) +
  labs(
    x = NULL, 
    y = "[kg/ha]", 
    title = "Gesamtbiomasse der Bachforelle pro Hektar"
  ) +
  theme_bw() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

  # - Total Biomass kg / 100m 

bar_bio_100_bf <- ggplot(mean_river_est_species_output %>% 
                           filter(species == "Salmo trutta"), 
                         aes(x = river_name, y = biomass_per_100m_kg_mean)) + 
  geom_col(fill = "grey") + 
  #geom_errorbar(
   # aes(
     # ymin = pmax(biomass_per_100m_kg_mean - sd_biomass_per_100m_kg, 0), 
    #  ymax = biomass_per_100m_kg_mean + sd_biomass_per_100m_kg
    #), 
   # width = 0.2
  #) + 
  scale_x_discrete(limits = river_order) +
  labs(
    x = NULL,
    y = "[kg/100m]", 
    title = "Gesamtbiomasse der Bachforelle pro 100 m"
  ) +
  theme_bw() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

  # - Plot all with patchwork

bar_N_ha_bf 
bar_N__100_bf 
bar_bio_ha_bf 
bar_bio_100_bf
```

####5.6.5.2. Regenbogenforelle

```{r}
#Regenbogenforelle



# - Total Individuals per ha

bar_N_ha_rbf <-  ggplot(mean_river_est_species_output %>% 
                         filter(species == "Oncorhynchus mykiss"),
                       aes(x = river_name, y = N_per_ha_mean)) + 
  geom_col(fill = "grey") + 
  geom_errorbar(
    aes(
      ymin = N_per_ha_mean - sd_N_per_ha, 
      ymax = N_per_ha_mean + sd_N_per_ha
    ), 
    width = 0.2
  ) + 
  scale_x_discrete(limits = river_order) +
  labs(
    x = NULL,
    y = "[Individuen/ha]", 
    title = "Individuendichte der Regenbogenforelle pro Hektar"
  ) +
  theme_bw() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

  
  # - Total Individuals per 100 m 
bar_N__100_rbf <- ggplot(mean_river_est_species_output %>% 
                          filter(species == "Oncorhynchus mykiss"),
                        aes(x = river_name, y = N_per_100m_mean)) + 
  geom_col(fill = "grey") + 
  geom_errorbar(
    aes(
      ymin = N_per_100m_mean - sd_N_per_100m, 
      ymax = N_per_100m_mean + sd_N_per_100m
    ), 
    width = 0.2
  ) + 
  scale_x_discrete(limits = river_order) +
  labs(
    x= NULL, 
    y = "[Individuen/100m]", 
    title = "Individuendichte der Regenbogenforelle pro 100 m"
  ) +
  theme_bw() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )



  # - Total Biomass ka / ha

bar_bio_ha_rbf <- ggplot(mean_river_est_species_output %>% 
                          filter(species == "Oncorhynchus mykiss"),
                         aes(x = river_name, y = biomass_kg_ha_mean)) + 
  geom_col(fill = "grey") + 
  geom_errorbar(
    aes(
      ymin = pmax(biomass_kg_ha_mean - sd_biomass_kg_ha, 0) , 
      ymax = biomass_kg_ha_mean + sd_biomass_kg_ha
    ), 
    width = 0.2
  ) + 
  scale_x_discrete(limits = river_order) +
  labs(
    x = NULL, 
    y = "[kg/ha]", 
    title = "Gesamtbiomasse der Regenbogenforelle pro Hektar"
  ) +
  theme_bw() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

  # - Total Biomass kg / 100m 

bar_bio_100_rbf <- ggplot(mean_river_est_species_output %>% 
                           filter(species == "Oncorhynchus mykiss"),
                         aes(x = river_name, y = biomass_per_100m_kg_mean)) + 
  geom_col(fill = "grey") + 
  geom_errorbar(
    aes(
      ymin = pmax(biomass_per_100m_kg_mean - sd_biomass_per_100m_kg, 0), 
      ymax = biomass_per_100m_kg_mean + sd_biomass_per_100m_kg
    ), 
    width = 0.2
  ) + 
  scale_x_discrete(limits = river_order) +
  labs(
    x = NULL,
    y = "[kg/100m]", 
    title = "Gesamtbiomasse der Regenbogenforelle pro 100 m"
  ) +
  theme_bw() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

  # - Plot all with patchwork

bar_N_ha_rbf 
bar_N__100_rbf 
bar_bio_ha_rbf 
bar_bio_100_rbf
```

####5.6.5.2. Äsche

```{r}
#Äsche

# - Total Individuals per ha

bar_N_ha_thy <-  ggplot(mean_river_est_species_output %>% 
                         filter(species == "Thymallus thymallus") ,
                       aes(x = river_name, y = N_per_ha_mean)) + 
  geom_col(fill = "grey") + 
  geom_errorbar(
    aes(
      ymin = N_per_ha_mean - sd_N_per_ha, 
      ymax = N_per_ha_mean + sd_N_per_ha
    ), 
    width = 0.2
  ) + 
  scale_x_discrete(limits = river_order) +
  labs(
    x = NULL,
    y = "[Individuen/ha]", 
    title = "Individuendichte der Äsche pro Hektar"
  ) +
  theme_bw() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

  
  # - Total Individuals per 100 m 
bar_N__100_thy <- ggplot(mean_river_est_species_output %>% 
                          filter(species == "Thymallus thymallus") %>% 
                          mutate(
                           river_name = factor(river_name, levels = river_order)
                         ),
                        aes(x = river_name, y = N_per_100m_mean)) + 
  geom_col(fill = "grey") + 
  geom_errorbar(
    aes(
      ymin = N_per_100m_mean - sd_N_per_100m, 
      ymax = N_per_100m_mean + sd_N_per_100m
    ), 
    width = 0.2
  ) + 
  scale_x_discrete(limits = river_order) +
  labs(
    x= NULL, 
    y = "[Individuen/100m]", 
    title = "Individuendichte der Äsche pro 100 m"
  ) +
  theme_bw() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )



  # - Total Biomass ka / ha

bar_bio_ha_thy <- ggplot(mean_river_est_species_output %>% 
                          filter(species == "Thymallus thymallus"),     
                         aes(x = river_name, y = biomass_kg_ha_mean)) + 
  geom_col(fill = "grey") + 
  geom_errorbar(
    aes(
      ymin = pmax(biomass_kg_ha_mean - sd_biomass_kg_ha, 0), 
      ymax = biomass_kg_ha_mean + sd_biomass_kg_ha
    ), 
    width = 0.2
  ) + 
    scale_x_discrete(limits = river_order) +
  labs(
    x = NULL, 
    y = "[kg/ha]", 
    title = "Gesamtbiomasse der Äsche pro Hektar"
  ) +
  theme_bw() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

  # - Total Biomass kg / 100m 

bar_bio_100_thy <- ggplot(mean_river_est_species_output %>% 
                           filter(species == "Thymallus thymallus"),
                         aes(x = river_name, y = biomass_per_100m_kg_mean)) + 
  geom_col(fill = "grey") + 
  geom_errorbar(
    aes(
      ymin = pmax(biomass_per_100m_kg_mean - sd_biomass_per_100m_kg, 0), 
      ymax = biomass_per_100m_kg_mean + sd_biomass_per_100m_kg
    ), 
    width = 0.2
  ) + 
  scale_x_discrete(limits = river_order) +
  labs(
    x = NULL,
    y = "[kg/100m]", 
    title = "Gesamtbiomasse der Regenbogenforelle pro 100 m"
  ) +
  theme_bw() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

  # - Plot

bar_N_ha_thy
bar_N__100_thy 
bar_bio_ha_thy 
bar_bio_100_thy









```

#/
## 5.3. - ÖFG150 Abundance for totals and share of species


```{r}

## Calculate abundance and biomass per totals of each site - estimate species abundance by share of totals. 


site_slc_total <- dat_75 %>% 
  group_by(river_name, site_name) %>% 
  summarise(
    C1_site = sum(Run_1, na.rm = TRUE), 
    C2_site = sum(Run_2, na.rm = TRUE),
    fished_length = first(fished_length), 
    fished_width = first(fished_width), 
    fished_area = first(fished_area), 
    area_ha = first(area_ha), 
    n_species = n_distinct(species), 
    weight_real_kg = sum(weight_kg, na.rm = TRUE), 
    species_total = first(species_total),
    .groups = "drop"
  ) %>% 
  mutate(
    est = map2(C1_site, C2_site, seber_le_cren_est)
  ) %>% 
  unnest(est) %>% 
  mutate(
    #Abundance estimates per ha, 100 meter 
    N_site = N,
    N_per_ha = ifelse(area_ha > 0, N_site / area_ha, NA_real_), 
    N_per_100m = ifelse(fished_length > 0, N_site / fished_length * 100, NA_real_)
  )



species_prop <- dat_75 %>% 
  left_join(
    site_slc_total %>% 
      select(river_name, site_name, C1_site, C2_site, N_site, N_per_ha, N_per_100m), 
    by = c("river_name", "site_name")) %>% 
  group_by(river_name, site_name) %>% 
  mutate(
    #Abundance
    species_share = species_total / sum(species_total, na.rm = TRUE), 
    N_prop = N_site * species_share, 
    N_prop_per_ha = N_prop / area_ha, 
    N_prop_per_100m = N_prop / fished_length * 100, 
    #Biomass
    N_calc = N_prop - species_total, 
    weight_calc_kg = N_calc * median_species_weight_g / 1000, 
    biomass_prop_kg = weight_kg + weight_calc_kg, 
    biomass_prop_kg_ha = ifelse(area_ha > 0, biomass_prop_kg / area_ha, NA_real_), 
    biomass_prop_kg_100m = ifelse(fished_length > 0, biomass_prop_kg / fished_length * 100, NA_real_)
  ) %>% 
  ungroup() %>% 
  select(
    river_name, 
    site_name, 
    species, 
    area_ha, 
    fished_length, 
    Run_1, 
    Run_2, 
    species_total,
    C1_site, 
    C2_site, 
    N_site, 
    N_per_ha, 
    N_per_100m, 
    species_share, 
    N_prop, 
    N_prop_per_ha, 
    N_prop_per_100m,
    weight_kg,
    weight_calc_kg,
    biomass_prop_kg,
    biomass_prop_kg_ha, 
    biomass_prop_kg_100m, 
    
  )

#Add Sum of weight of all species to Seber-LeCren per site 


weight_sum_site <- species_prop %>% 
  group_by(site_name) %>% 
  summarise(
    biomass_site_total_kg = sum(biomass_prop_kg, na.rm = TRUE)
  )
 

site_slc_total <- site_slc_total %>% 
  left_join(weight_sum_site, by = "site_name") %>% 
  mutate(
    biomass_kg_ha = biomass_site_total_kg / area_ha, 
    biomass_kg_100m = biomass_site_total_kg /fished_length * 100
  )


#Show results 

site_slc_total


species_prop

```

### 5.3.1 Export as xlsx

```{r}

# Round values N to integer, kg to 2 decimals 


site_slc_total_round <- site_slc_total %>% 
  mutate(
    #Abundance and estimates
    N_site = round(N_site, 0),
    N_min = round(N_min, 0),
    N_max = round(N_max, 0),
    Var_N = round(Var_N, 0),
    sd_N = round(sd_N, 0),
    CI_95 = round(CI_95, 0),
    #Abundance per ha and 100 m 
    N_per_ha = round(N_per_ha, 0),
    N_per_100m = round(N_per_100m, 0),
    # Biomass 
    weight_real_kg = round(weight_real_kg, 3),
    biomass_site_total_kg = round(biomass_site_total_kg, 3),
    biomass_kg_ha = round(biomass_kg_ha, 2),
    biomass_kg_100m = round(biomass_kg_100m, 2)
  )
    

#Round species table 

species_prop_round <- species_prop %>% 
  mutate(
    #Abundance
    N_prop = round(N_prop, 0),
    #Share of species of total catch
    species_share = round(species_share, 2),
    #Abundance per ha and 100m
    N_prop_per_ha = round(N_prop_per_ha, 0),
    N_prop_per_100m = round(N_prop_per_100m, 0),
    #Biomass
    weight_kg = round(weight_kg, 3),
    weight_calc_kg = round(weight_calc_kg, 3),
    biomass_prop_kg = round(biomass_prop_kg, 3),
    biomass_prop_kg_ha = round(biomass_prop_kg_ha, 2),
    biomass_prop_kg_100m = round( biomass_prop_kg_100m, 2)
  )
  
# Write outputs ----> add your output path and desired name of excel document

#out_path <- "C:/Users/lenagraf/Documents/Seafile/ÖFG 150/4 Auswertungen/20260904_Stock_Site(ohneSchneider).xlsx"

#writexl::write_xlsx(
 # list(
 #   species_site = species_prop_round,
 #   total_site    = site_slc_total_round
#  ),
#  path = out_path
#)


```


### 5.3.2. Bar charts per site and river 


```{r}

#Totals per site N/ha

bar_N_ha_site <- ggplot(site_slc_total, aes(x = site_name, y = N_per_ha)) + 
  geom_col(fill = "royalblue3") + 
  labs(
    x = NULL,
    y = "[Individuen/ha]", 
    title = "Gesamtindividuendichte pro Hektar"
  ) +
  theme_bw() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )



 # - Total Individuals per 100 m 
bar_N_100_site <- ggplot(site_slc_total, aes(x = site_name, y = N_per_100m)) + 
  geom_col(fill = "royalblue3") + 
  labs(
    x= NULL, 
    y = "[Individuen/100m]", 
    title = "Gesamtindividuendichte pro 100 m"
  ) +
  theme_bw() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )



  # - Total Biomass ka / ha

bar_bio_ha_site <- ggplot(site_slc_total, aes(x = site_name, y = biomass_kg_ha)) + 
  geom_col(fill = "royalblue3") + 
  labs(
    x = NULL, 
    y = "[kg/ha]", 
    title = "Gesamtbiomasse pro Hektar"
  ) +
  theme_bw() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

  # - Total Biomass kg / 100m 

bar_bio_100_site <- ggplot(site_slc_total, aes(x = site_name, y = biomass_kg_100m)) + 
  geom_col(fill = "royalblue3") + 
  labs(
    x = NULL,
    y = "[kg/100m]", 
    title = "Gesamtbiomasse pro 100 m"
  ) +
  theme_bw() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

#Plot all 

bar_N_ha_site + bar_N_100_site 

bar_bio_ha_site + bar_bio_100_site



#Export as jpeg 

#ggsave("plots/Total_Nha_site.jpg", bar_N_ha_site, width = 10, height = 5, units = "in", dpi = 300)

#ggsave("plots/Total_N100m_site.jpg", bar_N_100_site, width = 10, height = 5, units = "in", dpi = 300)

#ggsave("plots/Total_kgha_site.jpg", bar_bio_ha_site, width = 10, height = 5, units = "in", dpi = 300)

#ggsave("plots/Total_kg100m_site.jpg", bar_bio_100_site, width = 10, height = 5, units = "in", dpi = 300)



```

###5.3.2.1. Species estimates per site - Bar charts

```{r}

##stacked bar charts N per ha per site 

bar_species_site_Nha <- ggplot(species_prop, 
                               aes(x = site_name, y = N_prop_per_ha, fill = species)) + 
  geom_col() + 
  scale_fill_manual(
    values = c(
      "Cottus gobio" = "#BFBFBF", 
      "Barbatula barbatula" = "#968F32", 
      "Barbus barbus" = "#EBB3E4", 
      "Oncorhynchus mykiss" = "#F9B47B", 
      "Squalius cephalus" = "#82C6D8", 
      "Gobio gobio" = "#96B6B8", 
      "Salmo trutta" = "#A1BF65", 
      "Phoxinus phoxinus" = "#E5BFB6", 
      "Hucho hucho" = "#8A8A8F", 
      "Thymallus thymallus" = "#A38DCF", 
      "Alburnoides bipunctaus" = "#CDF58B", 
      "Chondrostoma nasus" = "#80483C",
      "Salvelinus fontinalis" = "#EAEAEB",
      "Salvelinus alpinus × fontinalis" = "#CC9900"
    )
  ) +
  labs(
    x = "Stelle", 
    y = "[Individuen/ha]",
    title = "Individuendichte pro Stelle",
    fill = "Art"
  ) + 
  theme_bw() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.text = element_text(face = "italic")
  )

bar_species_site_Nha

## stacked bar charts - biomass per species per site 


bar_species_site_biomass <- ggplot(species_prop, 
                               aes(x = site_name, y = biomass_prop_kg_ha, fill = species)) + 
  geom_col() + 
  scale_fill_manual(
    values = c(
      "Cottus gobio" = "#BFBFBF", 
      "Barbatula barbatula" = "#968F32", 
      "Barbus barbus" = "#EBB3E4", 
      "Oncorhynchus mykiss" = "#F9B47B", 
      "Squalius cephalus" = "#82C6D8", 
      "Gobio gobio" = "#96B6B8", 
      "Salmo trutta" = "#A1BF65", 
      "Phoxinus phoxinus" = "#E5BFB6", 
      "Hucho hucho" = "#8A8A8F", 
      "Thymallus thymallus" = "#A38DCF", 
      "Alburnoides bipunctaus" = "#CDF58B", 
      "Chondrostoma nasus" = "#80483C",
      "Salvelinus fontinalis" = "#EAEAEB",
      "Salvelinus alpinus × fontinalis" = "#CC9900"
    )
  ) +
  labs(
    x = "Stelle", 
    y = "[kg/ha]",
    title = "Biomasse pro Stelle",
    fill = "Art"
  ) + 
  theme_bw() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.text = element_text(face = "italic")
  )



#Plot 

bar_species_site_Nha
bar_species_site_biomass


##Export 

ggsave("plots/Individuendichten pro Stelle mit arten.jpg", bar_species_site_Nha, width = 10, height = 5, units = "in", dpi = 300)

ggsave("plots/Biomasse pro Stelle mit Arten.jpg", bar_species_site_biomass, width = 10, height = 5, units = "in", dpi = 300)

                        

```




###5.3.3. Mean per river 


```{r}
mean_river_total <- site_slc_total %>%
  group_by(river_name) %>%
  summarize(
    N_per_ha_m = mean(N_per_ha, na.rm = TRUE),
    sd_N_per_ha = sd(N_per_ha, na.rm = TRUE),
    N_per_100m_m = mean(N_per_100m, na.rm = TRUE), 
    sd_N_per_100m = sd(N_per_100m, na.rm = TRUE),
    n_sites = n(),
    biomass_kg_ha_m = mean(biomass_kg_ha, na.rm = TRUE), 
    sd_biomass_kg_ha = sd(biomass_kg_ha, na.rm = TRUE),
    biomass_per_100m_kg_m = mean(biomass_kg_100m, na.rm = TRUE),
    sd_biomass_per_100m_kg = sd(biomass_kg_100m, na.rm = TRUE),
    .groups = "drop"
  )

mean_river_total
```



###5.3.3. Mean per species and River 


```{r}


#Calculate mean abundance and biomass for each river for each species each site per river represented in equal proportions 
##take into account all sites, sites with 0 individuals of a species will be calculated into the mean

species_prop_complete <- species_prop %>%
  select(river_name, site_name, species, N_prop, N_prop_per_ha, N_prop_per_100m, biomass_prop_kg_ha, biomass_prop_kg_100m) %>%
  mutate(
    species = as.character(species), 
    site_name = as.character(site_name)) %>% 
  group_by(river_name) %>%
  complete(
    site_name, 
    species, 
    fill = list(N_prop_per_ha = 0, N_prop_per_100m = 0, biomass_prop_kg_ha = 0, biomass_prop_kg_100m  = 0)
  ) %>%
  ungroup()


mean_river_species_prop <- species_prop_complete %>%
  group_by(river_name, species) %>%
  summarise(
    N_prop = mean(N_prop, na.rm = TRUE),
    N_prop_per_ha_m = mean(N_prop_per_ha, na.rm = TRUE),
    sd_N_prop_per_ha = sd(N_prop_per_ha, na.rm = TRUE),
    N_prop_per_100m_m = mean(N_prop_per_100m, na.rm = TRUE),
    sd_N_prop_per_100m = sd(N_prop_per_100m, na.rm = TRUE),
    n_sites = n(),
    n_present = sum(N_prop_per_ha > 0),
    biomass_prop_kg_ha_m = mean(biomass_prop_kg_ha, na.rm = TRUE), 
    sd_biomass_prop_kg_ha = sd(biomass_prop_kg_ha, na.rm = TRUE), 
    biomass_prop_kg_100m_m = mean(biomass_prop_kg_100m, na.rm = TRUE), 
    sd_biomass_prop_kg_100m = sd(biomass_prop_kg_100m, na.rm = TRUE), 
    .groups = "drop"
  )

# Beispiel: Ein Fluss
mean_river_species_prop %>%
  filter(river_name == "Erlauf Tormäuer") %>%
  arrange(desc(N_prop_per_ha_m))

```

#### 5.3.3.1 Export to xlsx. 

```{r}

#round values 

mean_river_total_round <- mean_river_total %>% 
  mutate(
    #Abundance and estimates
    n_sites = round(n_sites, 0),
    #Abundance per ha and 100 m 
    N_per_ha = round(N_per_ha_m, 0),
    sd_N_per_ha = round(sd_N_per_ha, 0),
    N_per_100m = round(N_per_100m_m, 0),
    sd_N_per_100m = round(sd_N_per_100m),
    # Biomass 
    biomass_kg_ha = round(biomass_kg_ha_m, 2),
    sd_biomass_kg_ha = round(sd_N_per_ha, 2), 
    biomass_per_100m_kg = round(biomass_per_100m_kg_m, 2), 
    sd_N_per_100m = round(sd_biomass_per_100m_kg, 2)
  )
    

#Round species table 

mean_river_species_prop_round <- mean_river_species_prop %>% 
  mutate(
    #Abundance
    N_prop = round(N_prop, 0),
    #Abundance per ha and 100m
    N_prop_per_ha = round(N_prop_per_ha_m, 0),
    sd_N_prop_per_ha = round(sd_N_prop_per_ha, 0), 
    N_prop_per_100m = round(N_prop_per_100m_m, 0),
    sd_N_prop_per_100m = round(sd_N_prop_per_100m, 0),
    #Biomass
    biomass_prop_kg_ha = round(biomass_prop_kg_ha_m, 2),
    sd_biomass_prop_kg_ha = round(sd_biomass_prop_kg_ha, 2), 
    biomass_prop_kg_100m = round( biomass_prop_kg_100m_m, 2), 
    sd_biomass_prop_kg_100m = round(sd_N_prop_per_100m, 2)
  )








# Write outputs ----> add your output path and desired name of excel document

#out_path <- "C:/Users/lenagraf/Documents/Seafile/ÖFG 150/4 Auswertungen/20260904_Stock_River_Mean.xlsx"

#writexl::write_xlsx(
#  list(
#    species_per_site = mean_river_species_prop_round,
#    total_per_site    = mean_river_total_round
#  ),
#  path = out_path
#)

```

#### 5.3.3.2. Bar charts river mean

```{r}

bar_N_ha_river <- ggplot(mean_river_total_round, aes(x = river_name, y = N_per_ha)) + 
  geom_col(fill = "royalblue3") + 
  #geom_errorbar(
   # aes(
    #  ymin = pmax(mean_N_per_ha - sd_N_per_ha, 0),
     # ymax = mean_N_per_ha + sd_N_per_ha
    #),
    #width = 0.2
  #) +
  labs(
    x = NULL,
    y = "[Individuen/ha]", 
    title = "Mittlere Gesamtindividuendichte pro Hektar"
  ) +
  theme_bw() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )



bar_N_100m_river <- ggplot(mean_river_total_round, aes(x = river_name, y = N_per_100m)) + 
  geom_col(fill = "royalblue3") + 
  #geom_errorbar(
   # aes(
    #  ymin = pmax(mean_N_per_100m - sd_N_per_100m, 0),
    #  ymax = mean_N_per_100m + sd_N_per_100m
    #),
    #width = 0.2
  #) +
  labs(
    x = NULL,
    y = "[Individuen/100m]", 
    title = "Mittlere Gesamtindividuendichte pro 100m"
  ) +
  theme_bw() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

bar_biomass_100m_river <- ggplot(mean_river_total_round, aes(x = river_name, y = biomass_per_100m_kg)) + 
  geom_col(fill = "royalblue3") + 
#  geom_errorbar(
 #   aes(
 #     ymin = pmax(mean_biomass_per_100m_kg - sd_biomass_per_100m_kg, 0),
  #    ymax = mean_biomass_per_100m_kg + sd_biomass_per_100m_kg
   # ),
    #width = 0.2
#  ) +
  labs(
    x = NULL,
    y = "[kg/100m]", 
    title = "Mittlere Gesamtbiomasse pro 100m"
  ) +
  theme_bw() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )


bar_biomass_ha_river <- ggplot(mean_river_total_round, aes(x = river_name, y = biomass_kg_ha)) + 
  geom_col(fill = "royalblue3") + 
  #geom_errorbar(
   # aes(
    #  ymin = pmax(mean_biomass_kg_ha - sd_biomass_kg_ha, 0),
    #  ymax = mean_biomass_kg_ha + sd_biomass_kg_ha
  #  ),
  #  width = 0.2
  #) +
  labs(
    x = NULL,
    y = "[kg/ha]", 
    title = "Mittlere Gesamtbiomasse pro Hektar"
  ) +
  theme_bw() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )



bar_N_ha_river

bar_N_100m_river

bar_biomass_100m_river

bar_biomass_ha_river


#Export as jpeg 

#ggsave("plots/Total_Nha_river.jpg", bar_N_ha_river, width = 8, height = 5, units = "in", dpi = 300)

#ggsave("plots/Total_N100m_river.jpg", bar_N_100m_river, width = 8, height = 5, units = "in", dpi = 300)

#ggsave("plots/Total_kgha_river.jpg", bar_biomass_ha_river, width = 8, height = 5, units = "in", dpi = 300)

#ggsave("plots/Total_kg100m_river.jpg", bar_biomass_100m_river, width = 8, height = 5, units = "in", dpi = 300)




```

####5.3.3.3.Stacked Bar Charts - N/ha & kg/ha


```{r}

bar_species_river_Nha <- ggplot(mean_river_species_prop_round, 
                               aes(x = river_name, y = N_prop_per_ha_m, fill = species)) + 
  geom_col() + 
  scale_fill_manual(
    values = c(
      "Cottus gobio" = "#BFBFBF", 
      "Barbatula barbatula" = "#968F32", 
      "Barbus barbus" = "#EBB3E4", 
      "Oncorhynchus mykiss" = "#F9B47B", 
      "Squalius cephalus" = "#82C6D8", 
      "Gobio gobio" = "#96B6B8", 
      "Salmo trutta" = "#A1BF65", 
      "Phoxinus phoxinus" = "#E5BFB6", 
      "Hucho hucho" = "#8A8A8F", 
      "Thymallus thymallus" = "#A38DCF", 
      "Alburnoides bipunctaus" = "#CDF58B", 
      "Chondrostoma nasus" = "#80483C",
      "Salvelinus fontinalis" = "#EAEAEB",
      "Salvelinus alpinus × fontinalis" = "#CC9900"
    )
  ) +
  labs(
    x = "Fluss", 
    y = "[Individuen/ha]",
    title = "Individuendichte pro Flussabschnitt",
    fill = "Art"
  ) + 
  theme_bw() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.text = element_text(face = "italic")
  )

bar_species_river_Nha

## stacked bar charts - biomass per species per site 


bar_species_river_biomass <- ggplot(mean_river_species_prop_round, 
                               aes(x = river_name, y = biomass_prop_kg_ha_m, fill = species)) + 
  geom_col() + 
  scale_fill_manual(
    values = c(
      "Cottus gobio" = "#BFBFBF", 
      "Barbatula barbatula" = "#968F32", 
      "Barbus barbus" = "#EBB3E4", 
      "Oncorhynchus mykiss" = "#F9B47B", 
      "Squalius cephalus" = "#82C6D8", 
      "Gobio gobio" = "#96B6B8", 
      "Salmo trutta" = "#A1BF65", 
      "Phoxinus phoxinus" = "#E5BFB6", 
      "Hucho hucho" = "#8A8A8F", 
      "Thymallus thymallus" = "#A38DCF", 
      "Alburnoides bipunctaus" = "#CDF58B", 
      "Chondrostoma nasus" = "#80483C",
      "Salvelinus fontinalis" = "#EAEAEB",
      "Salvelinus alpinus × fontinalis" = "#CC9900"
    )
  ) +
  labs(
    x = "Fluss", 
    y = "[kg/ha]",
    title = "Biomasse pro Flussabschnitt",
    fill = "Art"
  ) + 
  theme_bw() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.text = element_text(face = "italic")
  )



#Plot 

bar_species_river_Nha
bar_species_river_biomass


##Export 

#ggsave("plots/Individuendichten pro Fluss mit arten.jpg", bar_species_river_Nha, width = 10, height = 5, units = "in", dpi = 300)

#ggsave("plots/Biomasse pro Fluss mit Arten.jpg", bar_species_river_biomass, width = 10, height = 5, units = "in", dpi = 300)


```






####5.3.3.4. Bachforelle

```{r}
#Bachforelle 

river_order <- sort(unique(mean_river_species_prop$river_name))


# - Total Individuals per ha

bar_N_ha_bf_prop <-  ggplot(mean_river_species_prop_round %>% 
                         filter(species == "Salmo trutta"),
                       aes(x = river_name, y = N_prop_per_ha)) + 
  geom_col(fill = "royalblue3") + 
#  geom_errorbar(
#    aes(
#      ymin = mean_N_prop_per_ha - sd_N_prop_per_ha, 
#      ymax = mean_N_prop_per_ha + sd_N_prop_per_ha
#    ), 
#    width = 0.2
#  ) + 
  scale_x_discrete(limits = river_order) +
  labs(
    x = NULL,
    y = "[Individuen/ha]", 
    title = "Mittlere Individuendichte der Bachforelle pro Hektar"
  ) +
  theme_bw() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )


bar_N_ha_bf_prop


  # - Total Individuals per 100 m 
bar_N_100_bf_prop <- ggplot(mean_river_species_prop_round %>% 
                          filter(species == "Salmo trutta"),
                        aes(x = river_name, y = N_prop_per_100m)) + 
  geom_col(fill = "royalblue3") + 
#  geom_errorbar(
#    aes(
#      ymin = mean_N_prop_per_100m - sd_N_prop_per_100m, 
#      ymax = mean_N_prop_per_100m + N_prop_per_100m
#    ), 
#    width = 0.2
#  ) + 
  scale_x_discrete(limits = river_order) +
  labs(
    x= NULL, 
    y = "[Individuen/100m]", 
    title = "Individuendichte der Bachforelle pro 100 m"
  ) +
  theme_bw() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )



  # - Total Biomass ka / ha

bar_bio_ha_bf_prop <- ggplot(mean_river_species_prop_round %>% 
                          filter(species == "Salmo trutta"),
                        aes(x = river_name, y = biomass_prop_kg_ha)) + 
  geom_col(fill = "royalblue3") + 
 # geom_errorbar(
  #  aes(
   #   ymin = pmax(mean_biomass_prop_kg_ha - sd_biomass_prop_kg_ha, 0), 
    #  ymax = mean_biomass_prop_kg_ha + sd_biomass_prop_kg_ha
  #  ), 
  #  width = 0.2
#  ) + 
  scale_x_discrete(limits = river_order) +
  labs(
    x = NULL, 
    y = "[kg/ha]", 
    title = "Gesamtbiomasse der Bachforelle pro Hektar"
  ) +
  theme_bw() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

  # - Total Biomass kg / 100m 

bar_bio_100_bf_prop <- ggplot(mean_river_species_prop_round %>% 
                           filter(species == "Salmo trutta"), 
                         aes(x = river_name, y = biomass_prop_kg_ha)) + 
  geom_col(fill = "royalblue3") + 
#  geom_errorbar(
#    aes(
#      ymin = pmax(mean_biomass_prop_kg_ha - sd_biomass_prop_100m_kg, 0), 
#      ymax = mean_biomass_prop_kg_ha + sd_biomass_prop_100m_kg
#    ), 
#    width = 0.2
#  ) + 
  scale_x_discrete(limits = river_order) +
  labs(
    x = NULL,
    y = "[kg/100m]", 
    title = "Mittlere Gesamtbiomasse der Bachforelle pro 100 m"
  ) +
  theme_bw() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

  # - Plot all 

bar_N_ha_bf_prop
bar_N_100_bf_prop
bar_bio_ha_bf_prop
bar_bio_100_bf_prop

#Export to jpeg

#ggsave("plots/BF_Nha_river.jpg", bar_N_ha_bf_prop, width = 8, height = 5, units = "in", dpi = 300)

#ggsave("plots/BF_N100m_river.jpg", bar_N_100_bf_prop, width = 8, height = 5, units = "in", dpi = 300)

#ggsave("plots/BF_kgha_river.jpg", bar_bio_ha_bf_prop, width = 8, height = 5, units = "in", dpi = 300)

#ggsave("plots/BF_kg100m_river.jpg", bar_bio_100_bf_prop, width = 8, height = 5, units = "in", dpi = 300)


```

####5.3.3.4. Äsche

```{r}
#Äsche  

river_order <- sort(unique(mean_river_species_prop$river_name))


# - Total Individuals per ha

bar_N_ha_th_prop <-  ggplot(mean_river_species_prop_round %>% 
                         filter(species == "Thymallus thymallus"),
                       aes(x = river_name, y = N_prop_per_ha)) + 
  geom_col(fill = "royalblue3") + 
#  geom_errorbar(
#    aes(
#      ymin = mean_N_prop_per_ha - sd_N_prop_per_ha, 
#      ymax = mean_N_prop_per_ha + sd_N_prop_per_ha
#    ), 
#    width = 0.2
#  ) + 
  scale_x_discrete(limits = river_order) +
  labs(
    x = NULL,
    y = "[Individuen/ha]", 
    title = "Mittlere Individuendichte der Äsche pro Hektar"
  ) +
  theme_bw() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )



  # - Total Individuals per 100 m 
bar_N_100_th_prop <- ggplot(mean_river_species_prop_round %>% 
                          filter(species == "Thymallus thymallus"),
                        aes(x = river_name, y = N_prop_per_100m)) + 
  geom_col(fill = "royalblue3") + 
#  geom_errorbar(
#    aes(
#      ymin = mean_N_prop_per_100m - sd_N_prop_per_100m, 
#      ymax = mean_N_prop_per_100m + N_prop_per_100m
#    ), 
#    width = 0.2
#  ) + 
  scale_x_discrete(limits = river_order) +
  labs(
    x= NULL, 
    y = "[Individuen/100m]", 
    title = "Mittlere Individuendichte der Äsche pro 100 m"
  ) +
  theme_bw() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )



  # - Total Biomass ka / ha

bar_bio_ha_th_prop <- ggplot(mean_river_species_prop_round %>% 
                          filter(species == "Thymallus thymallus"),
                        aes(x = river_name, y = biomass_prop_kg_ha)) + 
  geom_col(fill = "royalblue3") + 
 # geom_errorbar(
  #  aes(
   #   ymin = pmax(mean_biomass_prop_kg_ha - sd_biomass_prop_kg_ha, 0), 
    #  ymax = mean_biomass_prop_kg_ha + sd_biomass_prop_kg_ha
  #  ), 
  #  width = 0.2
#  ) + 
  scale_x_discrete(limits = river_order) +
  labs(
    x = NULL, 
    y = "[kg/ha]", 
    title = "Mittlere Gesamtbiomasse der Äsche pro Hektar"
  ) +
  theme_bw() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

  # - Total Biomass kg / 100m 

bar_bio_100_th_prop <- ggplot(mean_river_species_prop_round %>% 
                           filter(species == "Thymallus thymallus"), 
                         aes(x = river_name, y = biomass_prop_kg_ha)) + 
  geom_col(fill = "royalblue3") + 
#  geom_errorbar(
#    aes(
#      ymin = pmax(mean_biomass_prop_kg_ha - sd_biomass_prop_100m_kg, 0), 
#      ymax = mean_biomass_prop_kg_ha + sd_biomass_prop_100m_kg
#    ), 
#    width = 0.2
#  ) + 
  scale_x_discrete(limits = river_order) +
  labs(
    x = NULL,
    y = "[kg/100m]", 
    title = "Mittlere Gesamtbiomasse der Äsche pro 100 m"
  ) +
  theme_bw() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

  # - Plot all 

bar_N_ha_th_prop
bar_N_100_th_prop
bar_bio_ha_th_prop
bar_bio_100_th_prop

#Export to jpeg

#ggsave("plots/Äsche_Nha_river.jpg", bar_N_ha_th_prop, width = 8, height = 5, units = "in", dpi = 300)

#ggsave("plots/Äsche_N100m_river.jpg", bar_N_100_th_prop, width = 8, height = 5, units = "in", dpi = 300)

#ggsave("plots/Äsche_kgha_river.jpg", bar_bio_ha_th_prop, width = 8, height = 5, units = "in", dpi = 300)

#ggsave("plots/Äsche_kg100m_river.jpg", bar_bio_100_th_prop, width = 8, height = 5, units = "in", dpi = 300)


```


#/
#6 - Compare share and estimated abundance

```{r}
##Combine species level and share 

comparison <- species_prop %>%
  select(river_name, site_name, species, N_prop, N_prop_per_ha, Run_1, Run_2) %>%
  left_join(
    slc_species %>%
      filter(ok) %>%
      select(river_name, site_name, species, N, N_per_ha),
    by = c("river_name", "site_name", "species")
  ) %>%
  rename(
    N_art = N,
    N_art_per_ha = N_per_ha
  )
##Scatterplot all black 
ggplot(comparison, aes(x = N_prop_per_ha, y = N_art_per_ha)) +
  geom_point(alpha = 0.5) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", colour = "red") +
  labs(
    x = "N/ha proportional (Site-SLC)",
    y = "N/ha artspezifisch (Art-SLC)",
    title = "Vergleich: Art-SLC vs. proportionale Schätzung"
  ) +
  theme_bw()


##Scatterplot per species 


ggplot(comparison, aes(x = N_prop_per_ha, y = N_art_per_ha, colour = species)) +
  geom_point(alpha = 0.6) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", colour = "red") +
  labs(
    x = "N/ha proportional",
    y = "N/ha artspezifisch",
    title = "Vergleich: Art-SLC vs. proportionale Schätzung"
  ) +
  theme_bw() +
  theme(legend.position = "bottom")


##Prozentuelle abweichung pro art
comparison_diff <- comparison %>%
  group_by(species) %>%
  summarise(
    sum_N_art = sum(N_art, na.rm = TRUE),
    sum_N_prop = sum(N_prop, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    diff_pct = (sum_N_art - sum_N_prop) / sum_N_prop * 100
  )

ggplot(comparison_diff, aes(x = species, y = diff_pct)) +
  geom_col(fill = "tomato") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(
    x = NULL,
    y = "Abweichung [%]",
    title = "Abweichung: Summe(Art-SLC) vs. Site-SLC"
  ) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

##in welcher art sind die abweichungen ? 

comparison_river <- comparison %>%
  group_by(species) %>%
  summarise(
    mean_N_art = mean(N_art_per_ha, na.rm = TRUE),
    mean_N_prop = mean(N_prop_per_ha, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  pivot_longer(
    cols = c(mean_N_art, mean_N_prop),
    names_to = "method",
    values_to = "N_per_ha"
  ) %>%
  mutate(
    method = ifelse(method == "mean_N_art", "Art-SLC", "Proportional")
  )

ggplot(comparison_river, aes(x = species, y = N_per_ha, fill = method)) +
  geom_col(position = "dodge") +
  labs(
    x = NULL,
    y = "[Individuen/ha]",
    fill = "Methode",
    title = "Vergleich: Art-SLC vs. Proportional pro Fluss"
  ) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

comparison %>%
  filter(is.na(N_art)) %>%
  select(river_name, site_name, species, N_prop, N_art, Run_1, Run_2)


comparison_status <- comparison %>%
  mutate(
    status = case_when(
      is.na(N_art) ~ "Art-SLC nicht möglich",
      abs(N_art - N_prop) < 0.01 ~ "identisch",
      N_art > N_prop ~ "Art-SLC höher",
      N_art < N_prop ~ "Art-SLC niedriger"
    ),
    diff_pct = ifelse(N_prop > 0, (N_art - N_prop) / N_prop * 100, NA_real_)
  )

# Zusammenfassung
comparison_status %>%
  count(status)


ggplot(comparison_status, aes(x = N_prop_per_ha, y = N_art_per_ha, colour = status)) +
  geom_point(alpha = 0.6, size = 2) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", colour = "red") +
  labs(
    x = "N/ha proportional",
    y = "N/ha artspezifisch",
    colour = "Status",
    title = "Vergleich mit Problemfällen"
  ) +
  theme_bw() +
  theme(legend.position = "bottom")

```



#/
#7 - Length-Frequency Plots

## 7.1. Split Dataset into Rivers

```{r}

data_river_list <- data %>% 
  group_by(river_name) %>% 
  group_split()

river_names <- data %>% 
  distinct(river_name) %>% 
  pull(river_name)

names(data_river_list) <- river_names

```


## 7.2. N label for plot
```{r}
N_LF <-
  data %>%
  group_by(river_name, species) %>% 
  summarise(N = n(), .groups = "drop") %>% 
  mutate(
    label = paste0("N = ", N))

N_LF
```



## 7.3. LF Overview over all species in one River

```{r}


#Length frequency plots for all species in each river
##No fixed scales


LF_plot_overview <- data %>% 
  group_by(river_name) %>% ##insert site_name etc
  group_map(~ {
    river <- .y$river_name
    df_river <- .x
    text_river <- N_LF %>% 
      filter(river_name == river)
    
    ggplot(df_river,
         aes(total_length)) +
      
  
  geom_histogram(
                 binwidth = 20,
                 boundary = 0,
                 color ="black",
                 position ="stack") +

  scale_x_continuous(
    name = "total length [mm]",
    ) +
  
  scale_y_continuous(name = "number of individuals",
                     ) +
  
  theme_classic() +
    
  ggtitle(.y$river_name) +
  
  theme(
    plot.title = element_text(size = 14),
    axis.title.x = element_text(size = 14),
    axis.title.y = element_text(size = 14),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    legend.text = element_text(size = 11)
  ) +
  
  facet_wrap(~ species, scales = "free") + 
      
      
  geom_text(data = text_river, aes(x = Inf, y = Inf, label = label), inherit.aes = FALSE, size = 5, hjust = 1.1, vjust = 1.1) 
    
    
  })

names(LF_plot_overview) <- data %>% 
  distinct(river_name) %>% 
  pull(river_name)


##plot all

for (p in LF_plot_overview) {
  print(p)
  }


```
## 7.4. Adapt the LF to specific needs

```{r}
#Function for Length frequency

plot_length_freq <- function(data, 
                              facet_var = "species",
                              color_var = NULL,
                              binwidth = 20,
                              x_breaks = NULL,
                              x_limits = NULL,
                              title = NULL,
                              show_n = TRUE,
                              free_scales = "free") {
  
  if (is.null(title)) title <- ""
  
  # N-Label
  if (show_n) {
    if (!is.null(color_var)) {
      text_df <- data %>%
        group_by(.data[[facet_var]], .data[[color_var]]) %>%
        summarise(n = n(), .groups = "drop") %>%
        group_by(.data[[facet_var]]) %>%
        summarise(label = paste(paste0(.data[[color_var]], ": n=", n), collapse = "\n"), .groups = "drop")
    } else {
      text_df <- data %>%
        group_by(.data[[facet_var]]) %>%
        summarise(label = paste0("n = ", n()), .groups = "drop")
    }
  }
  
  # Basis-Aesthetics
  if (!is.null(color_var)) {
    p <- ggplot(data, aes(x = total_length, fill = .data[[color_var]]))
  } else {
    p <- ggplot(data, aes(x = total_length))
  }
  
  p <- p +
    geom_histogram(
      binwidth = binwidth,
      boundary = 0,
      color = "black",
      alpha = 0.7,
      position = "stack"
    ) +
    scale_x_continuous(
      name = "Total length [mm]",
      breaks = if (!is.null(x_breaks)) x_breaks else waiver(),
      limits = x_limits
    ) +
    scale_y_continuous(name = "Number of individuals") +
    theme_classic() +
    ggtitle(title) +
    theme(
      plot.title = element_text(size = 14),
      axis.title = element_text(size = 14),
      axis.text = element_text(size = 12),
      legend.text = element_text(size = 11),
      strip.text = element_text(face = "italic", size = 12)
    ) +
    facet_wrap(as.formula(paste("~", facet_var)), scales = free_scales)
  
  if (show_n) {
    p <- p + geom_text(
      data = text_df,
      aes(x = Inf, y = Inf, label = label),
      inherit.aes = FALSE,
      size = 4, hjust = 1.1, vjust = 1.1
    )
  }
  
  return(p)
}

##Plot desired length-frequency diagram 
##add needed values
##add filter 
##color_var = plot different values in different colors
##x_breaks = define breaks. e.g. x_breaks = seq(0,600, 50): min = 0, max = 600, breaks by 50mm
##free_scales: 


BF_Schwarza <- data %>% 
  filter(river_name == "Schwarza") %>% 
  filter(species == "Salmo trutta") %>% 
  plot_length_freq(
    facet_var = "site_name", 
    binwidth = 25,
    x_breaks = seq(0, 600, 50), 
    free_scales = "fixed",
    title = "Bachforelle"
  )

BF_Schwarza


```


#### export
```{r}
#ggsave("LF_plot.jpg", LF_plot, width = 8, height = 5, units = "in", dpi = 300)
```

#/
#8 - DeLury - share of species

```{r}

##Total DeLury over all species 

site_del_total <- dat_75 %>% 
  group_by(river_name, site_name) %>% 
  summarise(
    C1_site = sum(Run_1, na.rm = TRUE), 
    C2_site = sum(Run_2, na.rm = TRUE),
    C3_site = sum(Run_3, na.rm = TRUE),      
    fished_length = first(fished_length), 
    fished_width  = first(fished_width), 
    fished_area   = first(fished_area), 
    area_ha       = first(area_ha), 
    n_species     = n_distinct(species), 
    weight_real_kg = sum(weight_kg, na.rm = TRUE), 
    species_total  = first(species_total),
    .groups = "drop"
  ) %>% 
  mutate(
    est = pmap(list(C1_site, C2_site, C3_site), ~ delury_est(c(...)))
  ) %>% 
  unnest(est) %>% 
  mutate(
    N_site      = N,
    N_per_ha    = ifelse(area_ha > 0, N_site / area_ha, NA_real_), 
    N_per_100m  = ifelse(fished_length > 0, N_site / fished_length * 100, NA_real_)
  )

##Proportional calculation of N per species 

species_prop_del <- dat_75 %>% 
  left_join(
    site_del_total %>% 
      select(river_name, site_name, N_site, N_per_ha, N_per_100m), 
    by = c("river_name", "site_name")
  ) %>% 
  group_by(river_name, site_name) %>% 
  mutate(
    species_share   = species_total / sum(species_total, na.rm = TRUE), 
    N_prop          = N_site * species_share, 
    N_prop_per_ha   = N_prop / area_ha, 
    N_prop_per_100m = N_prop / fished_length * 100, 
    
    N_calc            = N_prop - species_total, 
    weight_calc_kg    = N_calc * median_species_weight_g / 1000, 
    biomass_prop_kg   = weight_kg + weight_calc_kg, 
    biomass_prop_kg_ha   = ifelse(area_ha > 0, biomass_prop_kg / area_ha, NA_real_), 
    biomass_prop_kg_100m = ifelse(fished_length > 0, biomass_prop_kg / fished_length * 100, NA_real_)
  ) %>% 
  ungroup()

weight_sum_site_del <- species_prop_del %>% 
  group_by(site_name) %>% 
  summarise(biomass_site_total_kg = sum(biomass_prop_kg, na.rm = TRUE))

site_del_total <- site_del_total %>% 
  left_join(weight_sum_site_del, by = "site_name") %>% 
  mutate(
    biomass_kg_ha   = biomass_site_total_kg / area_ha, 
    biomass_kg_100m = biomass_site_total_kg / fished_length * 100
  )


```

